---
title: "Chlorurus Data"
author: "Peter Carlson"
date: "12/10/2021"
output: word_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(EMLassemblyline)
library(flextable)

```

Please **revise and fill in** as much information as possible. Fields highlighted in yellow must be completed.


The information in this document will be used to create the EML of the data package to be published on the [Environmental Data Initiative (EDI) repository](https://portal.edirepository.org/nis/home.jsp).

## 1. Data Package Title




## 2. Dataset Title
<!--_Include what, where, and when in the dataset title_-->
 - Chlorurs Activity Palmyra 2014
 - Chlorurus Area Palmyra 2014
 - Fish Information Chlorurs Data
 

## 3. Abstract
_Please provide an abstract specifically of the dataset. This is different from the abstract of an associated publication. Include what, why, where, when, and how_

[See example here](https://docs.google.com/document/d/1KdHJObHl5Bxxr9t0LISTwX0cCSVvx7NPUjz5T_P9JEc/edit#)

 


## 4. Creators
_These are the people who will show up as authors in the dataset citation. These are the individuals who have provided intellectual or other significant contributions to the creation of this dataset. **Please add a row with the information of each individual that should be part of the authorship of this dataset.**_

**We highly encourage you to create an ORCID if you don't already have one.** [Find more information here.](https://info.orcid.org/what-is-orcid/)

```{r, creator table, echo = FALSE, message= FALSE, warning= FALSE}

first_name <- c("Peter", "")
middle_in <- c("", "")
last_name <- c("Carlson", " ")
organization <- c("University of California Santa Barbara", "")
email <- c("peter.carlson@ucsb.edu", "")
orcid <- c("", "")

creator_colname <- c("First Name", "Middle Initial", "Last Name", "Organization", "email address", "ORCID ID")

creator_table <- tibble(first_name, middle_in, last_name, organization, email, orcid)

colnames(creator_table) <- creator_colname

```


```{r, creators table export, echo=FALSE, message= FALSE, warning= FALSE, results = 'asis'}

set_flextable_defaults(big.mark = " ", 
  font.size = 10, 
  theme_fun = theme_box)


flextable::flextable(creator_table) %>% 
  width(width = 1)
  #autofit(add_w = 0.1, add_h = 0.1, part = c("body", "header"), unit = "in")
```


## 5. Other personnel names and roles 

_Who should a data user contact with questions about this data?_
_There must be at least one person or organization name to serve as the contact for this dataset._
_You may also list other personnel who participated in the project (such as field crew, lab tech, data entry, etc.) in this table with optional fields, email addresses, organization, and ORCID ID._


**We highly encourage you to create an ORCID if you don't already have one.** [Find more information here.](https://info.orcid.org/what-is-orcid/)


```{r, personnel table, echo = FALSE, message= FALSE, warning= FALSE}

p_first_name <- c("Peter", "Camila")
p_middle_in <- c("", "")
p_last_name <- c("Carlson", "Vargas Poulsen")
p_organization <- c("University of California Santa Barbara", "PADL Data Manager, University of California Santa Barbara")
p_email <- c("peter.carlson@ucsb.edu", "camilavargas@ucsb.edu")
p_orcid <- c("", "")
p_role <- c("contact", "associated party")

personnel_colnames <- c("First Name", "Middle Initial", "Last Name", "Organization", "email address", "ORCID ID", "Role in project")


personnel_table <- tibble(p_first_name, p_middle_in, p_last_name, p_organization, p_email, p_orcid, p_role)

colnames(personnel_table) <- personnel_colnames

```


```{r, personnel table export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(personnel_table) %>% 
  width(width = 1)
```


## 6. License 
_**Please highlight** the license for the release of your data. Click on the license name for more information._ 

[CCO](https://creativecommons.org/publicdomain/zero/1.0/)

Public Domain Dedication, aka “No Rights Reserved.” This one means, “If I hold copyright in this, I waive it. And if we’re dealing with a country where we can’t waive copyright, here’s a broad public license with no attribution requirement. And just as a backup, I also promise not to sue you for copyright or related stuff if you use this.”

**Message for user:** Please keep the dataset creators informed of any plans to use the dataset. Consultation with the original investigators is strongly encouraged. Publications and data products that make use of the dataset should include proper acknowledgement.

or

[CC BY](https://creativecommons.org/licenses/by/4.0/)

Attribution is required. CC licenses require that those who reuse a work provide attribution to the work’s creator by retaining “identification of the creator(s) of the Licensed Material and any others designated to receive attribution, in any reasonable manner requested by the Licensor (including by pseudonym if designated).”

**Message for user:** Data user is required to cite it appropriately in any publication that results from its use. The Data User should realize that these data may be actively used by others for ongoing research and that coordination may be necessary to prevent duplicate publication. The Data User is urged to contact the authors of these data if any questions about methodology or results occur. Where appropriate, the Data User is encouraged to consider collaboration or co-authorship with the authors. The Data User should realize that misinterpretation of data may occur if used out of context of the original study. While substantial efforts are made to ensure the accuracy of data and associated documentation, complete accuracy of data sets cannot be guaranteed. All data are made available "as is." The Data User should be aware, however, that data are updated periodically and it is the responsibility of the Data User to check for new versions of the data. The data authors and the repository where these data were obtained shall not be liable for damages resulting from any use or misinterpretation of the data.

## 7. Keywords
_Using keywords from a controlled vocabulary (CV) will improve your data's future discovery and reuse.  The LTER CV is a good source for keywords. Access the [LTER CV here](https://vocab.lternet.edu/vocab/vocab/index.php).  Also, please determine one or two keywords that best describe your lab, station, and/or project (e.g., Trout Lake Station, NTL LTER).). Add as many rows to this table as needed_

- Palmyra Atoll
- Chlorurus
- 




## 8. Funding of this work
_List only the main PI of a grant that supported this project, starting with the main grant first.  Add rows to the table if several grants were involved._


```{r, funding table, echo = FALSE, message= FALSE, warning= FALSE, message= FALSE, warning= FALSE}

pi_first_name <- " "
pi_middle_in <- " "
pi_last_name <- " "
pi_email <- " "
pi_orcid <- " "
title_grant <- " "
fund_agency <- " "
fund_id <- " "

fund_colnames <- c("PI First Name", "PI Middle Initial", "PI Last Name", "PI email", "PI ORCID ID", "Title of Grant", "Funding Agency", "Funding Identification Number")


funding_table <- tibble(pi_first_name, pi_middle_in, pi_last_name, pi_email, pi_orcid, title_grant, fund_agency, fund_id)

colnames(funding_table) <- fund_colnames

```


```{r, funding table export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(funding_table) %>% 
  width(width = 1)
  
```



## 9. Timeframe

```{r, timefram table, echo = FALSE, message= FALSE, warning= FALSE}

Information <- c("Begin date", "End date", "Is data collection ongoing or completed?")

Description <- c("2014", "2014", "Completed")

timeframe_table <- tibble(Information, Description)

flextable::flextable(timeframe_table) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")

```



## 10. Geographic location

_Use decimal degrees to define a point or a bounding box._
Every point you add will be displayed on a map once the data package is published. [See example here](https://portal.edirepository.org/nis/mapbrowse?scope=knb-lter-sbc&identifier=108)

**Verbal description:** Palmyra Atoll

```{r, geographic location table, echo = FALSE, message= FALSE, warning= FALSE}

Directions <- c("Northbound", "Southbound", "Eastbound", "Westbound")

Coordinate <- c(5.88333, 5.871, -162.043, -162.083)

geo_loc_table <- tibble(Directions, Coordinate)

flextable(geo_loc_table) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")

```

**Copy this block to add multiple points or areas.**_

**Verbal description:**


```{r, geographic location table 2, echo = FALSE, message= FALSE, warning= FALSE}

coordinate <- c(" ", " ", " ", " ")

geo_loc_table_2 <- tibble(Directions, coordinate)

flextable(geo_loc_table_2) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")

```

## 11. Methods
_Be specific about the study design and field and lab methods for collecting and processing the data. Include instrument descriptions and protocol citations._

Find an example [in this link](https://docs.google.com/document/d/1KdHJObHl5Bxxr9t0LISTwX0cCSVvx7NPUjz5T_P9JEc/edit#)



## 12. Data Provenance

_Is this data derived from other data? If so, you will want to document this information, so users know where this data came from.  Please specify the source datasets used in the below provenance table, preferably with their DOI or URL.  [Here is an example of a dataset derived from several others](https://portal.edirepository.org/nis/mapbrowse?packageid=edi.101.3)._



```{r, data provenance, echo = FALSE, message= FALSE, warning= FALSE}

data_title <- c(" ", " ")
data_doi_url <- c("", "")
creator_name <- c("", "")
contact_email <- c("", "")

provenance_colnames <- c("Dataset title", "Dataset DOI or URL", "Creator Name", "Contact Email")


provenance_table <- tibble(data_title, data_doi_url, creator_name, contact_email)

colnames(provenance_table) <- provenance_colnames

```


```{r, provence table, export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(provenance_table) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
```



## 13. Data Table

Each row in the below table describes one column in your data table.  Complete each row as follows:

- **Description:** Please give a specific definition of the column name. This can be lengthy.
- **Unit:** Identify units for all numeric variables. All rows where there is an * under the unit column must be filled in with a unit.
- **Date format:** Please tell us exactly how the date and time are formatted: e.g., mm/dd/yyyy hh:mm:ss, plus the time zone and whether daylight savings were observed.  ISO date format of YYYY-MM-DD or YYYY-MM-DD hh:mm:ss is preferred.
- **Missing value code:** If a code for ‘no data’ is used, please specify: e.g., -99999, NA
- **Missing value code Explanation:** Why are these values missing? e.g.: value not available, value not recorded.


**Table name:** (Add a short name for this table)
**Table description:** (Add brief description of table contents)


```{r, create data attributes tables, echo = FALSE, message= FALSE, warning= FALSE}

## Location of datasets in the package

path_data <- here::here("7.clean_data")
path_templates <- here::here("3.data_attributes")

#-----------------------------------------------------------------#


## If there is just one file in 7.clean_data run this code
## **UPDATE NAMES**

# file1_name <- "FILE NAME"
# 
# ## Creating the attribute .txt
# EMLassemblyline::template_table_attributes(
#   path = path_templates,
#   data.path = path_data,
#   data.table = paste0(file1_name, ".csv"))
# 
# ## reading text into a data frame
# data_attributes1 <- read.delim2(here::here(paste0("3.data_attributes/attributes_", file1_name, ".txt"))) %>% 
#   mutate(unit = case_when(unit == "!Add units here!" ~ "*"))

#------------------------------------------------------------------#

## If there is more than one data set in 7.clean_data, run this code

## Create table with all the file names
files_names <- tibble(
  list.files(path_data, pattern = "csv")) %>% 
  rename(file_name = 1) %>% 
  mutate(file_name = str_remove(file_name, ".csv"),
         attribute_name = paste0("data_attributes", 1:n()),
         position = 1:n())

## Creating the attribute .txt

# for (i in files_names$file_name){
# 
#   EMLassemblyline::template_table_attributes(
#   path = path_templates,
#   data.path = path_data,
#   data.table = paste0(i, ".csv"))
# }

## reading text into a data frame

##General function
read_attribute <- function(test){
  
  read.delim2(here::here(paste0("3.data_attributes/attributes_", test, ".txt"))) %>% 
  mutate(unit = case_when(unit == "!Add units here!" ~ "*"))
}

## Loop to read and name each file 
for (i in files_names$position){
  
  assign(files_names$attribute_name[i], read_attribute(files_names$file_name[i]))

  }


```



```{r, attribute table 1, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(data_attributes1) %>% 
  width(width = 1)

```

<br>
```{r, attribute table 2, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(data_attributes2) %>% 
  width(width = 1)

```

<br>

```{r, attribute table 3, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(data_attributes3) %>% 
  width(width = 1)

```


## 14. Attributes code

_If you use codes in your column, please define each code in the following table. **Fill in only if necessary**_ 



```{r, attribute code, echo = FALSE, message= FALSE, warning= FALSE}


## Attributes list of Files
attributes_names <- tibble(
  list.files(path_templates, pattern = "attributes_")) %>% 
  rename(file_name = 1) %>% 
  mutate(file_name = str_remove(file_name, ".txt"),
         catvar_name = paste0("catvar", 1:n()),
         position = 1:n())

## Create catvars file

# for (i in attributes_names$file_name){
# 
#   EMLassemblyline::template_categorical_variables(
#   path = path_templates,
#   data.path = path_data)
# }

##General function
read_catvar <- function(test){
  
  read.delim2(here::here(paste0("3.data_attributes/catvars_", test, ".txt")))
}

## Loop to read and name each file 
for (i in attributes_names$position){
  
  assign(attributes_names$catvar_name[i], read_catvar(files_names$file_name[i]))

  }


```


```{r, categorical variables table 1, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(catvar1) %>%
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
  

```

<br>

```{r, categorical variables table 2, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(catvar2) %>%
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
  

```


<br>

```{r, categorical variables table 3, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(catvar3) %>%
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
  

```



## 17. Articles
_List articles citing this dataset. Add as many rows as necessary_


```{r, publications, echo = FALSE, message= FALSE, warning= FALSE}

doi <- " "
article_title <- " "
journal <- " "


publications_colnames <- c("Article DOI or URL (DOI is preferred)", "Article title", "Journal title")

publications <- tibble(doi, article_title, journal)

colnames(publications) <- publications_colnames

```


```{r, publications export, echo=FALSE, message= FALSE, warning= FALSE}

flextable::flextable(publications) %>% 
  autofit(add_w = 0.2, add_h = 0.1, part = c("body", "header"), unit = "in")
```


## Notes, Comments, and Questions
_Please let us know if you have any additional comments or questions about your data or the EML information. THANK YOU!_







